Fitness tracking reveals task-specific associations between memory, mental health, and exercise

### 2021-09-24 paper/main.tex
added some notes

\begin{itemize}
\item characterizing behaviors (color by quartile and continue the
  color scheme in later figures-- hue reflects task, shading reflects
  performance.  white outline means immediate, black outline means delayed)
  \begin{itemize}
  \item Free recall (immediate + delayed): pfr, lag-CRP, spc  (color:
    recall performance).  Note: for delayed pfr and spc, need to collapse
    across lists (current figure doesn't do this...).
    Figure~\ref{fig:fr_behavioral}.  Also collapse across lists for
    delayed analysis...
    \item Naturalistic recall (immediate + delayed): reproduce a version of the sherlock
      movie/recall trajectories (color: mean precision)
    \item Foreign language flashcards (immediate + delayed): p(correct) histogram (color: p(correct))
      \item Spatial learning: mean error by number of shapes (color:
        slope of line fit to errors as a function of the number of shapes)
      \end{itemize}
    \item Fitness info (break down by task performance, potentially
      separately for each task); also separate out recent (raw) and
      recent versus baseline -- color using same color scheme as
      behavior figure
      \begin{itemize}
      \item activity (steps, zone minutes, floors/elevation)
      \item resting heart rate
        \item sleep
        \end{itemize}
  \item exploratory analysis (correlations)
    \begin{itemize}
    \item Memory-memory
    \item fitness-fitness
    \item survey-survey
    \item (fitness + survey)-memory
    \end{itemize}
  \item predictive analysis (regressions)
    \begin{itemize}
    \item Predict memory performance on held-out task from other tasks
    \item Predict memory performance on each task using fitness data
      \item Predict memory performance on each task using survey data
      \end{itemize}
    \item Reverse correlations: look at recent changes versus baseline
      trends (color using same scheme as behavior figure)
      \begin{itemize}
      \item Fitness profile that predicts performance on each task (barplots + timelines)
      \item Fitness profile for each survey demographic (barplots + timelines)
        \begin{itemize}
          \item Select out mental health demographics (based on meds, stress levels)
          \end{itemize}
        \end{itemize}
  \end{itemize}

>>>>

\begin{itemize}
\item characterizing behaviors (color by quartile and continue the
  color scheme in later figures-- hue reflects task, shading reflects
  performance.  white outline means immediate, black outline means delayed)
  \begin{itemize}
  \item Free recall (immediate + delayed): pfr, lag-CRP, spc  (color:
    recall performance).  Note: for delayed pfr and spc, need to collapse
    across lists (current figure doesn't do this...).
    Figure~\ref{fig:fr_behavioral}.  Also collapse across lists for
    delayed analysis...
    \item Naturalistic recall (immediate + delayed): reproduce a version of the sherlock
      movie/recall trajectories (color: mean precision)
    \item Foreign language flashcards (immediate + delayed): p(correct) histogram (color: p(correct))
      \item Spatial learning: mean error by number of shapes (color:
        slope of line fit to errors as a function of the number of
        shapes)
      \end{itemize}
    \item Fitness info (break down by task performance, potentially
      separately for each task); also separate out recent (raw) and
      recent versus baseline -- color using same color scheme as
      behavior figure
      \begin{itemize}
      \item activity (steps, zone minutes, floors/elevation)
      \item resting heart rate
        \item sleep
        \end{itemize}
  \item exploratory analysis (correlations).  Possibly make some sort of scatter matrix or pairplot-- rows/columns:
          tasks.  Diagonal: histogram of performance metric for that
          task.  Above-diagonal entries: compare performance across
          tasks (by subject).  Below-diagonal entries: empty?
          density/2d histograms?
    \begin{itemize}
    \item Memory-memory
    \item fitness-fitness
    \item survey-survey
    \item (fitness + survey)-memory
    \end{itemize}
  \item predictive analysis (regressions)
    \begin{itemize}
    \item Predict memory performance on held-out task from other tasks
    \item Predict memory performance on each task using fitness data
      \item Predict memory performance on each task using survey data
      \end{itemize}
    \item Reverse correlations: look at recent changes versus baseline
      trends (color using same scheme as behavior figures).  Possibly 
      \begin{itemize}
      \item Fitness profile that predicts performance on each task (barplots + timelines)
      \item Fitness profile for each survey demographic (barplots + timelines)
        \begin{itemize}
          \item Select out mental health demographics (based on meds, stress levels)
          \end{itemize}
        \end{itemize}
  \end{itemize}
